My title

### 2024-08-09 paper/paper.qmd
Update model

## Methodology
The language and environment used for this analysis is R (R Core Team 2020), alongside the tidyverse (cite), rstanarm (cite), cansim (cite), knitr (cite), ggplot2 (cite), scales (cite), modelsummary (cite), and marginaleffects (cite) packages.

@@

* $y_i$ as the total expenditure in Canadian dollars in year i. 
* $cpi_i$ is the annual Consumer Price Index (CPI) for year i

### Multiple linear regression
The model we employ is:

@@

* $y_i$ as the total expenditure in Canadian dollars in year i. 
* $cpi_i$ is the annual Consumer Price Index (CPI) for year i
* $income_i$ is the number of people in Ontario earning an income

>>>>

## Methodology
The language and environment used for this analysis is R [@citeR], alongside the tidyverse (@tidyverse), rstanarm (@rstanarm), cansim [@cansim], ggplot2 [@ggplot2], scales [@scales], modelsummary [@modelsummary], and marginaleffects [@marginaleffects] packages.

@@

* $y_i$ is the continuous outcome variable, representing the total expenditure in Canadian dollars in year i. 
* $cpi_i$ is the predictor variable, representing the annual Consumer Price Index (CPI) for year i

### Multiple linear regression
The model we employed is:

@@

* $y_i$ is the continuous outcome variable, representing the total expenditure in Canadian dollars in year $i$. 
* $cpi_i$ is the predictor variable, representing the annual Consumer Price Index (CPI) for year $i$
* $income_i$ is the number of people earning an income in year $i$.
